---
title: "NBA(1)"
author: "Sahba Salarian"
date: '2019-02-22'
output: pdf_document
---

```{r setup, include=FALSE}

#install.packages("faraway")
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(fig.pos = 'H')
knitr::opts_chunk$set(warning=FALSE)
knitr::opts_chunk$set(message=FALSE)
library(xtable)
options(xtable.comment = FALSE)
library(knitr)
library(tidyverse)
library(ggplot2)
library(bestglm) 
library(stargazer)
library(corrplot)
library (car)
library (repr)
library (MASS)
library (leaps)
library(pROC)
library(ROCR)
```

#Introduction

The amount of the estrogen hormone as measured in a random sample of 
11 straight men and in a separate random sample 15 gay males.
Note this is not the same as a single random sample!
Our purpose is just to understand how the hormones levels are related in
two distinct populations.

This data is available in R, faraway::hormone and was discussed in Faraway's 
book *Extensions of the Linear Model*.

This dataset is of special interest because the data structure is quite
simple since there are only $p=2$ inputs and more importantly it
illustrates the case of perfect separation of classes.
Although this happens quite fairly rarely it is the motivation behind the
formulation of Support Vector Machines (SVM).
SVM is a powerful method for solving linear and non-linear regression
and classification problems with high dimensional data.

Input the data and convert to tibble for nice display:

```{r GETDATA, echo=TRUE}
NBA1 <-read.csv("/Users/sahba/Dropbox/Data Science/NBA longevity/nba_logreg.csv", header=T, stringsAsFactors=F)
```



```{r structure, echo=TRUE}
str(NBA1)
```

As the dataset structure shows, the first column includes character variables, the name of athletes played in the league. I will replace the names with unique ID variables as follow:


```{r ID }
#NBA1$Name <- c(as.factor(NBA1$Name))
#str(NBA1)
```

## Data engineering

```{r Omit NA , echo = FALSE}
NBA2 <- na.omit(NBA1)
```


#Train/Test Split:


```{r Test&train, echo = FALSE}
set.seed(798102) 
split <- sample (3, nrow (NBA2), replace= TRUE, prob = c (0.6, 0.2, 0.2))
train <- NBA2 [split==1,]
cv <- NBA2 [split==2,]
test <- NBA2 [split==3,]

```



```{r SCATTERPLOT, echo=FALSE, results = "asis", fig.cap = ",,,,,,"}
#Figure 1

#options(repr.plot.width=6, repr.plot.height=9)
#scatterplotMatrix(~TARGET_5Yrs+GP+ MIN+ PTS+ FGM+ FGA+ FG.+X3P.Made+ X3PA+ X3P.+FTM+ FT.+OREB +DREB +REB+ AST+ STL+ BLK+ TOV, data = NBA1)

```

The TARGET_5Yrs should be analyzed versus other information for each athlete: GP, MIN, PTS, FGM, FGA, FG.,X3P.Made, X3PA, X3P.,FTM, FTA,FT.,OREB, DREB, REB, AST, STL, BLK, TOV 



```{r Correlation Matrix, echo=FALSE,fig.caption="Correlation Matrix"}
M<- cor(train[,-1])
#install.packages("corrplot")
#corrplot(M, method="color")
corrplot(M, type="upper")

```


```{r CORRELATIONPLOT2, echo=FALSE, results = "asis", fig.width=20, fig.height=19, fig.cap = ",,,,,,"}

library(ggplot2)

library(GGally)

ggpairs(NBA1[,2:21], aes(color=factor(TARGET_5Yrs), alpha=0.75), lower=list(continuous="smooth"))+ theme_bw()+

labs(title=".......")+

theme(plot.title=element_text(face='bold',color='black',hjust=0.5,size=12))

```






##Use **glm()** to fit the model

```{r LogFit1, echo=TRUE}
LogFit1 <- glm(TARGET_5Yrs ~  GP+ MIN+ PTS+ FGM+ FGA+ FG.+X3P.Made+ X3PA+ X3P.+FTM+ FTA+ FT.+OREB +DREB +REB+ AST+ STL+ BLK+ TOV , data=train, family=binomial(link='logit'))
stargazer (LogFit1, type="latex", title="ANOVA test of the logistic Regresssion ", header = FALSE)
summary(LogFit1)

```
```{r Logistic Plot, echo=FALSE,fig.caption="ROC for Logistic"}
probTE<- predict(LogFit1,cv,type="response")
test_roc = roc(cv$TARGET_5Yrs~probTE, plot = TRUE, print.auc = TRUE,main="ROC for GLM")

```










#Decision Boundary



```{r, echo=TRUE}
hdata %>%
 ggplot(aes(x=an, y=estrogen)) +
 geom_point(aes(colour=orientation), size=3) +
 geom_abline(intercept=-0.93649, slope=1.1185) +
 geom_abline(intercept=-0.4592, slope=0.8769, colour="blue", linetype=2 )
```

